Precision calculations of the cosmic shear power spectrum projection

### 2017-02-16 cfhtlens.tex
MK: Replaced Legendre transform with spherical transform; added ref Peebles 73

For a first-order standard Limber flat-sky approximation (L1Fl) we find
$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$, the same
result that was published in \cite{CFHTLenS-2pt-notomo}. Using the second-order
extended Limber flat-sky hybrid approximation (ExtL2FlHyb) results in $\sigma_8
(\Omega_{\rm m}/0.27)^{0.6} = 0.788 \pm 0.032$, a negligible change of the
amplitude that is well within the Monte-Carlo sampling noise. \mk{The largest
difference is measured with the depreciated case ExtL1Fl, for which the
recovered amplitude is larger by $16\%$ of the statistical error.} \ch{These
negligible changes to the error bars were to be expected owing to the
high level of statistical noise and cosmic variance in comparison to the low-level impact of the various
approximations shown in Fig.~\ref{fig:Cl_cases}.}

>>>>

For a first-order standard Limber flat-sky approximation (L1Fl) we find
$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$, the same
result that was published in \cite{CFHTLenS-2pt-notomo}. Using the second-order
extended Limber flat-sky hybrid approximation (ExtL2FlHyb) results in $\sigma_8
(\Omega_{\rm m}/0.27)^{0.6} = 0.788 \pm 0.032$, a negligible change of the
amplitude that is well within the Monte-Carlo sampling noise. The largest
difference is measured with the depreciated case ExtL1Fl, for which the
recovered amplitude is larger by $16\%$ of the statistical error. \ch{These
negligible changes to the error bars were to be expected owing to the
high level of statistical noise and cosmic variance in comparison to the low-level impact of the various
approximations shown in Fig.~\ref{fig:Cl_cases}.}

### 2017-02-16 conclusions.tex
MK: Replaced Legendre transform with spherical transform; added ref Peebles 73

In this paper we evaluate precision theoretical calculations for cosmic shear
observables, bringing together different sources from the literature to provide
a pedagogical review of the impact of adopting flat-sky and Limber
approximations.  We demonstrate that for current surveys, such as CFHTLenS
\mk{and KiDS}, these approximations have a negligible impact on cosmological
parameter constraints.

@@

\mk{ We have considered a flat Universe throughout this paper. To generalise
the calculations to non-flat models, one needs to modify the comoving angular
diameter distance to account for the spatial curvature $K \ne 0$. In addition,
the spherical Bessel functions are replaced with hyperspherical Bessel
functions \citep{1986ApJ...308..546A}. In a universe with positive curvature
$K>0$ the 3D wave modes become discrete integer variables. For non-flat models,
we do however not expect qualitative differences from our results.}

>>>>

In this paper we evaluate precision theoretical calculations for cosmic shear
observables, bringing together different sources from the literature to provide
a pedagogical review of the impact of adopting flat-sky and Limber
approximations.  We demonstrate that for current surveys, such as CFHTLenS
and KiDS, these approximations have a negligible impact on cosmological
parameter constraints.

@@

We have considered a flat Universe throughout this paper. To generalise
the calculations to non-flat models, one needs to modify the comoving angular
diameter distance to account for the spatial curvature $K \ne 0$. In addition,
the spherical Bessel functions are replaced with hyperspherical Bessel
functions \citep{1986ApJ...308..546A}. In a universe with positive curvature
$K>0$ the 3D wave modes become discrete integer variables. For non-flat models,
we do however not expect qualitative differences from our results.
